The evolution of gene expression in the term placenta of viviparous mammals

### 2016-02-01 manuscript/manuscript.Rnw
add competing interests and acknowledgements

\section*{Acknowledgements}
  Text for this section \ldots

>>>>

  Amy Weckle performed all of the RNA extractions and managed the
  samples.

  Jason Caravas provided samples.

  Dalen Agnew provided samples.

  Kurt Benirschke provided samples.

  Sue Savage-Rumbaugh provided samples.

  Chong J. Kim provided samples.

  Günter P. Wagner provided samples.

  Roberto Romero provided samples.

  Derek E. Wildman conceived the study, wrote the paper, and performed
  analyses.

  \section*{Acknowledgements}
  The authors would like to specially acknowledge those groups whose
  publicly available data contributed to the completeness of this
  work.
